PS753

### 2022-02-09 _academics/ms797-glossary/ms797-glossary.Rmd
build

---
title: "MS797 Glossary"
description: |
  Glossary for MS797 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-30
output:
 distill::distill_article:
   self_contained: false
   toc: true
---

@@

<p style="background: #eee">
Academics &gt; [MS797](../ms797/index.html)
&gt; Glossary
</p>

>>>>

---
title: "MS797 Glossary"
description: |
  Glossary for MS797 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-30
output:
 distill::distill_article:
   self_contained: false
   toc: true
categories:
  - machine learning
  - glossary
---

@@

<p style="background: #eee">
[<i class="fas fa-home"></i>](/) &gt; Academics &gt; [MS797](../ms797/index.html)
&gt; Glossary
</p>

### 2022-02-09 _academics/ms797-useful-r-tidbits/ms797-useful-r-tidbits.Rmd
Add useful bits link
build

---
title: "Useful R tidbits: Machine Learning"
description: |
  Tasty R snacks that do useful things in Machine Learning
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-06
output:
  distill::distill_article:
    self_contained: false
    toc: true
preview: ISLR-cover.png
---

```{r setup, include=FALSE}
# knitr::opts_chunk$set(echo = FALSE)
```

@@

This document contains R snippets pertaining to work in the [Machine Learning class](../ms797/index.html). There is also one for the [Social Networks class](../px753/index.html).

>>>>

---
title: "Useful R tidbits: Machine Learning"
description: |
  Tasty R snacks that do useful things in Machine Learning
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-06
output:
  distill::distill_article:
    self_contained: false
    toc: true
preview: ISLR-cover.png
categories:
  - r
  - machine learning
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

This document contains R snippets pertaining to work in the [Machine Learning class](../ms797/index.html). There is also one for the [Social Networks class](../ps753-useful-r-tidbits/index.html).

### 2022-02-09 _academics/ms797/ms797.Rmd
build

---
title: "MS797"
description: |
  Machine Learning for Social Sciences, Spring 2022.
# author:
#   - name: Steve Linberg
# date: 2022-01-30
output:
  distill::distill_article:
    self_contained: false
citation: false
---

@@

<p style="background: #eee">
Academics &gt; MS797
</p>

@@

- My ongoing [glossary](../ms797-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.

>>>>

---
title: "MS797"
description: |
  Machine Learning for Social Sciences, Spring 2022.
# author:
#   - name: Steve Linberg
# date: 2022-01-30
output:
  distill::distill_article:
    self_contained: false
citation: false
categories:
  - machine learning
---

@@

<p style="background: #eee">
[<i class="fas fa-home"></i>](/) &gt; Academics &gt; MS797
</p>

@@

- My ongoing [glossary](../ms797-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
- Some [useful R tidbits](../ms797-useful-r-tidbits/index.html) from, or inspired by, the text.

### 2022-02-09 _academics/ps753-glossary/ps753-glossary.Rmd
build

---
title: "PS753 Glossary"
description: |
  Glossary for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
   toc: true
bibliography: PS753.bib
---

>>>>

---
title: "PS753 Glossary"
description: |
  Glossary for PS753 coursework
author:
  - name: Steve Linberg
    url: {}
date: 2022-01-29
output:
 distill::distill_article:
   self_contained: false
   toc: true
bibliography: PS753.bib
categories:
  - social networks
  - glossary
---

### 2022-02-09 _academics/ps753-useful-r-tidbits/ps753-useful-r-tidbits.Rmd
build

---
title: "Useful R tidbits: Social Networks"
description: |
  Tasty R snacks that do useful things in Social Networks
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-08
output:
  distill::distill_article:
    self_contained: false
    toc: true
---

>>>>

---
title: "Useful R tidbits: Social Networks"
description: |
  Tasty R snacks that do useful things in Social Networks
author:
  - name: Steve Linberg
    url: {}
date: 2022-02-08
output:
  distill::distill_article:
    self_contained: false
    toc: true
categories:
  - r
  - social networks
---

### 2022-02-09 _academics/ps753/ps753.Rmd
Add pseudo top-level nav for /academics
build
Add useful bits link

---
title: "PS753"
description: |
  Political and Social Networks, Spring 2022.
# author:
#   - name: Steve Linberg
# date: 2022-01-29
output:
  distill::distill_article:
    self_contained: false
citation: false
---

@@

<p style="background: #eee">
PS 753
</p>

@@

- My ongoing [glossary](../ps753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.

>>>>

---
title: "PS753"
description: |
  Political and Social Networks, Spring 2022.
# author:
#   - name: Steve Linberg
# date: 2022-01-29
output:
  distill::distill_article:
    self_contained: false
citation: false
categories:
  - social networks
---

@@

<p style="background: #eee">
[<i class="fas fa-home"></i>](/) &gt; Academics &gt; PS 753
</p>

@@

- My ongoing [glossary](../ps753-glossary/index.html) page; feel free to comment, or make additions or corrections via comments or github.
- Some [useful R tidbits](../ps753-useful-r-tidbits/index.html) from the course material and related sources.
